Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2015-01-18 ms.tex
capitalize AKARI as per referee suggestion
more about 143 GHz CO to placate referee
clean up

We apply the \cite{FDS99} two-component thermal dust emission model to the
\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as the
sum of two modified blackbodies serves as an important alternative to the 
commonly adopted single modified blackbody (MBB) dust emission model. Analyzing
the joint \PLANCK/DIRBE dust spectrum, we show that two-component models 
provide a better fit to the 100-3000 GHz emission than do single-MBB models, 
though by a lesser margin than found by \cite{FDS99} based on FIRAS and DIRBE. 
We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
temperature by fitting the two-component model to \PLANCK~217-857 GHz along 
with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
matches the dust spectrum near its peak, accounts for the flattening of the 
dust spectrum at millimeter wavelengths, and specifies dust temperature at 
6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
foreground predictions from 100 to 3000 GHz. We find that, in diffuse sky 
regions, our two-component 100-217 GHz predictions are on
average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
and 7.9\% at 217 GHz. We calibrate our two-component optical depth to 
reddening, and compare the resulting reddening estimates with 
those based on stellar spectra. We find imperfect zodiacal light subtraction in
both DIRBE/\IRAS~and \PLANCK~to be the dominant large angular scale systematic 
problem in our two-component temperature map and reddening estimates.

@@

\section{Introduction}
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. In the mid-infrared
and far-infrared, Galactic dust emission contributes significantly
to the total observed sky intensity. At optical and ultraviolet (UV) 
wavelengths, dust grains absorb and scatter starlight. Observations of 
interstellar dust emission/absorption can improve our understanding of the 
physical conditions and composition of the interstellar medium (ISM), an 
environment which plays a crucial role in Galactic evolution and star 
formation. Equally, or perhaps even more important to the practice of 
astronomy, however, is accurately accounting for dust as a foreground which 
reddens optical/UV observations of stars/galaxies and superimposes Galactic 
emission on low-frequency observations of the cosmic microwave background 
(CMB).

Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. The \textit{Infrared Astronomy 
Satellite} (\IRAS), with its $\sim$4$'$ resolution, revolutionized the study of
 Galactic dust emission, first revealing the high-latitude ``infrared cirrus'' 
using 60$\mu$m and 100$\mu$m observations \citep{low84, wheelock94}. Later, the
Diffuse Infrared Background Experiment (DIRBE) aboard the \COBE~satellite 
provided complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m, boasting a reliable zero point despite inferior 
$\sim$0.7$^{\circ}$ angular resolution \citep{boggess92}. \COBE/FIRAS 
\citep{firas} also provided full-sky infrared dust spectra at $7^{\circ}$ 
resolution in 213 narrow frequency bins between 30 GHz and 2850 GHz.

@@

\subsection{Compact Sources}
\label{sec:ptsrc}
After subtracting the SMICA CMB model, we interpolate over compact sources, 
including both point sources and resolved galaxies. Removing compact sources at
this stage is important as it prevents contamination of compact-source-free 
pixels in our downstream analyses which require smoothing of the \PLANCK~maps. 
SFD carefully removed point sources and galaxies from the \verb|i100| map 
everywhere outside of $|b|$$<$$5^{\circ}$. We do not perform any further 
modifications of the \verb|i100| map to account for compact sources. To mask 
compact sources in the \PLANCK~217-857 GHz maps, we use the SFD compact source 
mask. At 100, 143 GHz we use the compact source masks provided by the 
\PLANCK~collaboration in the file \verb|HFI_Mask_PointSrc_2048_R1.10.fits|. 
Given our pixelization (see $\S$\ref{sec:pix}), 1.56\% of pixels are masked 
at 217-857 GHz (1.05\%, 1.02\% at 100, 143 GHz).

>>>>

We apply the \cite{FDS99} two-component thermal dust emission model to the
\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as the
sum of two modified blackbodies serves as an important alternative to the 
commonly adopted single modified blackbody (MBB) dust emission model. Analyzing
the joint \PLANCK/DIRBE dust spectrum, we show that two-component models 
provide a better fit to the 100-3000 GHz emission than do single-MBB models, 
though by a lesser margin than found by \cite{FDS99} based on FIRAS and DIRBE. 
We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
temperature by fitting the two-component model to \PLANCK~217, 353, 545, and 
857 GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
matches the dust spectrum near its peak, accounts for the flattening of the 
dust spectrum at millimeter wavelengths, and specifies dust temperature at 
6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
foreground predictions from 100 GHz to 3000 GHz. We find that, in diffuse sky 
regions, our two-component 100-217 GHz thermal dust emission predictions are on
average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
and 7.9\% at 217 GHz. We calibrate our two-component optical depth to reddening
at visible wavelengths, and compare the resulting reddening estimates with 
those based on stellar spectra. We find imperfect zodiacal light subtraction in
both DIRBE/\IRAS~and \PLANCK~to be the dominant large angular scale systematic 
problem in our two-component temperature map and reddening estimates.

@@

\section{Introduction}
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. In the mid-infrared
and far-infrared, Galactic dust emission contributes significantly
to the total observed sky intensity. At optical and ultraviolet (UV) 
wavelengths, dust grains absorb and scatter starlight. Observations of 
interstellar dust emission/absorption can improve our understanding of the 
physical conditions and composition of the interstellar medium (ISM), an 
environment which plays a crucial role in Galactic evolution and star 
formation. Equally, or perhaps even more important to the practice of 
astronomy, however, is accurately accounting for dust as a foreground which 
reddens optical/UV observations of stars/galaxies and superimposes Galactic 
emission on low-frequency observations of the cosmic microwave background 
(CMB). 
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. The \textit{Infrared Astronomy 
Satellite} (\IRAS), with its $\sim$4$'$ resolution, revolutionized the study of
 Galactic dust emission, first revealing the high-latitude ``infrared cirrus'' 
using 60$\mu$m and 100$\mu$m observations \citep{low84, wheelock94}. Later, the
Diffuse Infrared Background Experiment (DIRBE) aboard the \COBE~satellite 
provided complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m, boasting a reliable zero point despite inferior 
$\sim$0.7$^{\circ}$ angular resolution \citep{boggess92}. \COBE/FIRAS 
\citep{firas} also provided full-sky infrared dust spectra at $7^{\circ}$ 
resolution in 213 narrow frequency bins between 30 GHz and 2850 GHz.

@@

\subsection{Compact Sources}
\label{sec:ptsrc}
After subtracting the SMICA CMB model, we interpolate over compact sources, 
including both point sources and resolved galaxies. Removing compact sources at
this stage is important as it prevents contamination of compact-source-free 
pixels in our downstream analyses which require smoothing of the \PLANCK~maps. 
SFD carefully removed point sources and galaxies from the \verb|i100| map 
everywhere outside of $|b|$$<$$5^{\circ}$. We do not perform any further 
modifications of the \verb|i100| map to account for compact sources. To mask 
compact sources in the \PLANCK~217-857 GHz maps, we use the SFD compact source 
mask. At 100, 143 GHz we use the compact source masks provided by the 
\PLANCK~collaboration in the file \verb|HFI_Mask_PointSrc_2048_R1.10.fits|. 
Given our pixelization (see $\S$\ref{sec:pix}), 1.56\% of pixels are masked 
at 217-857 GHz (1.05\%, 1.02\% at 100, 143 GHz)
